Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-27 Thesis/01-chap1.Rmd
add comb

@@

>>>>

Function `calc_p_value_comb()` from the package `visage` can be used to compute $p$-values of $V_{K-j}$. The first argument is `detected`, which needs to be a vector of Boolean values denoting whether the observer detects the actual data plot. Desired number of evaluations and number of selections need to be provided via argument `n_eval` and `n_sel`.

For example, given a visual test $V_3$ where the first observer selects one plot and gets correct, the second observer selects one plot but misses, and the third observer selects two plots and gets correct. The $p$-value of all possible outcomes of $V_2$ can be computed using the following code:

```{r}
set.seed(10086)
```

```{r echo = TRUE}
calc_p_value_comb(detected = c(TRUE, FALSE, TRUE), 
                  n_eval = 2, 
                  n_sel = c(1, 1, 2))
```

`calc_p_value_comb()` returns a vector of $p$-value along with an attribute which is a matrix representing elements being used by the specific outcome. Elements in the first column indicates that the first observer and the second observer are involved in the visual test, and the corresponding $p$-value is $0.09352$.

@@

### Power Estimation

###
